% Chapter 16
\chapter{PACKET RADIO REVIEW - QUIZ}
In this chapter, let's do some reviewing. I'm going to present a short quiz on packet radio covering the basics that I've presented in the past 15 chapters. Let's see how well you can answer the following questions without looking back for the answers. In chapter 17 I'll discuss each question and give you the correct answers.\\

\begin{enumerate}
\item What are the three TNC modes of communication?
  \begin{enumerate}
  \item Connect, Converse, Terminal
  \item Command, Converse, Terminal
  \item Command, Converse, Transparent
  \item Command, Connect, Transparent
  \end{enumerate}
\item What TNC command is used to set the transmit path for beacons and CQs?
\item What is the TNC command CHECK used for?
\item While you're connected to another station, what command is used to monitor other traffic on the frequency?
\item If you saw one of the following lines on your screen when in monitor mode, what would the asterisk indicate?
  \begin{itemize}
  \item W6ABC-3>N6XYZ,W6PW-1*: Hi Bob
  \item W6ABC-3>W6PW-1*>N6XYZ: Hi Bob
  \end{itemize}
(Displays vary with various TNCs, so both common types are shown.)
\item Why does the packet node network improve communications compared to the use of digipeaters?
\item If you're connected to a station in New Mexico using the node network, how do you disconnect?
\item If N6ZYX-2 connected to you via a node, what would the SSID of the station become at your end of the connection?
\item When you're connected to another station, what are the two most probable causes for packets to NOT be received by the other station?
\item There are several basic commands used on a packet bulletin board system. Indicate what you would enter to perform the following:
  \begin{enumerate}
  \item Receive a list of messages.
  \item Read message 47134.
  \item Download a file in the General (ID G) directory called FCCEXAMS.LST.
  \item Enter a personal message to Jim, WA6DDM, who uses the W6PW BBS in San Francisco, California.
  \item Change your home BBS from W9ABC to W7XYZ.
  \end{enumerate}

\item To send an NTS message via packet addressed to Tom Smith, 123 Main Street, Keene, NH 03431, telephone (603) 555-4321, what would you enter at the BBS prompt?
\item If a message has a STATUS of BF, what does that indicate?
\item When sending a bulletin, what is the most important thing to remember when entering the SUBJECT?
\item If you wanted to send a message to your friend John, W4IP, but you didn't know what the call of his home BBS was, what could you do to try to find out what the call is?
\item What is the maximum value for MAXFRAME? If you're working a station on 30 meters and are sending a lot of retries, should you increase or decrease MAXFRAME?

\end{enumerate}

Well, how did you think you did? We'll take a look at the answers to these questions and more in chapter 17.